Between Subgraph Isomorphism and Maximum Common Subgraph

### 2017-02-01 poster/poster.tex

The \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to  subgraph of two graphs simultaneously---the size of the maximum common subgraph gives us a measure of how similar two graphs are.

>>>>

The \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to
a subgraph of two graphs simultaneously---the size of the maximum common subgraph gives us a measure of how similar two graphs are.
